Experiment 5: Replication Analysis

### 2024-10-22 group-e/E5-analysis-replication.Rmd
fixes to get figures to display and cross-ref correctly

```{r}
# Excluding Subjects
all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
E5.excluded.n = 8

@@

```{r groupEMain, fig.show="hold", out.width="45%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:groupEMain-caption)"}
# All defaults
include_graphics("figGroupEOrigA")
include_graphics("figGroupEOrigB")
plot.A
plot.R
```

Following Shimojo and colleagues, data for each condition were fit using a four-parameter sigmoid (Fig. \@ref(fig:Shimojo)). These fit less well than in the original paper for both the attractiveness judgment (R^2^ = `r round(R2.A,2)` vs. 0.91) and the roundness judgment (R^2^ = `r round(R2.R,2)` vs. 0.91).

>>>>

```{r}
# Excluding Subjects (AJ: why/how? I can't figure it out, so I'm putting them back in)
# all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
# E5.excluded.n = 8

#There's an issue with Subject 603ea6a51c38def3e4140ba6: their webgazer_data is a list of length 0 instead of a dataframe like the others.
all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6")

@@

```{r groupEMain, fig.show="hold", out.width="45%", echo=FALSE, message=FALSE, warning=FALSE, fig.cap="(ref:groupEMain-caption)"}
# All defaults
include_graphics("figGroupEOrigA.png")
include_graphics("figGroupEOrigB.png")
plot.A
plot.R
```

Following Shimojo and colleagues, data for each condition were fit using a four-parameter sigmoid (Fig. \@ref(fig:groupEMain)). These fit less well than in the original paper for both the attractiveness judgment (R^2^ = `r round(R2.A,2)` vs. 0.91) and the roundness judgment (R^2^ = `r round(R2.R,2)` vs. 0.91).
